\section{Related Work}
\label{sec:related_work}

% Discuss existing work in several categories:


\subsection{NEED TO DO}
\paragraph{Predictive Maintenance Techniques.}
Overview of common PdM approaches:
\begin{itemize}
    \item Physics-based models (if relevant, briefly).
    \item Statistical models (e.g., ARIMA, Survival Analysis).
    \item Traditional Machine Learning (SVM, RF, Regression for RUL).
    \item Deep Learning approaches (RNN, LSTM, CNN, Transformers for RUL prediction). Mention how they typically use the standard RUL target. Cite key papers.
\end{itemize}

\paragraph{Work on CMAPSS Dataset.}
Review how the CMAPSS dataset has been used previously:
\begin{itemize}
    \item Focus on RUL prediction (mention state-of-the-art results/methods if known). Cite the Kaggle links/papers provided.
    \item Any work on fault diagnostics or classification using CMAPSS (though less common than RUL).
    \item Highlight that most works use the provided RUL labels, contrasting with your approach.
\end{itemize}

\paragraph{Clustering for Degradation Analysis.}
Discuss the use of clustering in PdM or related fields:
\begin{itemize}
    \item Clustering time-series data.
    \item Identifying operational modes or health states.
    \item Anomaly detection using clustering.
    \item Cite relevant studies, potentially outside CMAPSS if needed.
\end{itemize}

\paragraph{Hybrid Models in PdM.}
Review approaches that combine different modeling techniques:
\begin{itemize}
    \item Combining classification and regression.
    \item Ensemble methods.
    \item Fusion of physics-based and data-driven models.
    \item Position your work within this context – combining clustering-derived labels with classification/regression.
\end{itemize}

\paragraph{Risk Assessment in PdM.}
Discuss how risk or criticality is assessed in maintenance:
\begin{itemize}
    \item Existing risk scoring methods.
    \item Use of probabilities in decision making.
    \item Contrast with your proposed Risk Score formulation.
\end{itemize}

% Conclude by summarizing the gap your work addresses (custom multi-stage labeling, hybrid prediction, risk score on CMAPSS).


% ======================================================================
